Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-06-20 paper/gd1.tex
typos

\figurename~\ref{fig:orbitfit} shows \changes{a $1 \textrm{Gyr}$ segment of} the best-fitting orbit from the procedure outlined above.
The GD-1 stream crosses the midplane at large radius, far from the bulk of the
stellar density:
the grey line in the left panel shows the radius that contains $\approx 90\%$ of
the mass, assuming a \citet{Bovy:2012} model of the stellar disk.
% an exponential radial density profile with a scale radius
% $\rm R_d = 3~\kpc$ (an intermediate value of recent measurements, e.g.,
% \citealt{Bovy:2012}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{density-model.pdf}
\end{center}
\caption{
\emph{Top row}: Density of stars in $\phi_2$ (grey) and inferred density (black curve) for regions around the spur, blob, and a control field.
The model for the density includes components for the stream, background, and a feature overdensity (the spur or the blob), but with amplitudes that are allowed to go to zero (see \sectionname~\ref{sec:res_gap} for more details.)
\emph{Bottom row}: Inferred posterior probability distributions over the amplitude ($\alpha$) of each component in each field: $\alpha_{\textrm{s}}$ for the stream, $\alpha_{\textrm{bg}}$ for the background, and $\alpha_{\textrm{f}}$ for the feature.
In both feature fields, the model prefers an additional component to describe the feature, whereas in the control field the density is consistent with stream + background.
}
\label{fig:density-model}
\end{figure}

>>>>

\figurename~\ref{fig:orbitfit} shows \changes{a $1\,\textrm{Gyr}$ segment of} the best-fitting orbit from the procedure outlined above.
The GD-1 stream crosses the midplane at large radius, far from the bulk of the
stellar density:
the grey line in the left panel shows the radius that contains $\approx 90\%$ of
the mass, assuming a \citet{Bovy:2012} model of the stellar disk.
% an exponential radial density profile with a scale radius
% $\rm R_d = 3~\kpc$ (an intermediate value of recent measurements, e.g.,
% \citealt{Bovy:2012}).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{density-model.pdf}
\end{center}
\caption{
{\bf \emph{Top row}: Density of stars in $\phi_2$ (grey) and inferred density (black curve) for regions around the spur, blob, and a control field.
The model for the density includes components for the stream, background, and a feature overdensity (the spur or the blob), but with amplitudes that are allowed to go to zero (see \sectionname~\ref{sec:res_gap} for more details.)
\emph{Bottom row}: Inferred posterior probability distributions over the amplitude ($\alpha$) of each component in each field: $\alpha_{\textrm{s}}$ for the stream, $\alpha_{\textrm{bg}}$ for the background, and $\alpha_{\textrm{f}}$ for the feature.
In both feature fields, the model prefers an additional component to describe the feature, whereas in the control field the density is consistent with stream + background.}
}
\label{fig:density-model}
\end{figure}
